Changing Flights In The Air\\ (Abortable Chain Agreement)

### 2015-05-12 paper/paper.tex
Note about lattice agreement
Notes plus fixed typos

Our notion of Composable Generalized Consensus defines a common interface and a common correctness property for a round, abstracting over the particular round implementations and making all rounds compatible with each other. 
Moreover, our interface for rounds enable a straightforward crucial optimization seen in practical systems: introducing an external reconfiguration master which manages the addition of new replicas and the removal of failed ones. Interestingly, as explained in \cite{LamportMalkhiZhou09VerticalPaxosPrimarybackupReplication}, in a real system it is often possible to implement a reliable reconfiguration master which allows to tolerate $f$ faults with $f+1$ replicas instead of the traditional $2f+1$ replicas .

@@

    We present a new abstraction, Abortable Generalized Consensus, which enables the
    correct-by-construction composition of heterogeneous State-Machine
    Replication algorithms.

@@

@@

@@

>>>>

Our notion of Composable Generalized Consensus defines a common interface and a common correctness property for a round, abstracting over the particular round implementations and making all rounds compatible with each other. 
Moreover, our interface for rounds enable a straightforward crucial optimization seen in practical systems: introducing an external reconfiguration master which manages the addition of new replicas and the removal of failed ones. Interestingly, as explained in \cite{LamportMalkhiZhou09VerticalPaxosPrimarybackupReplication}, in a real system it is often possible to implement a reliable reconfiguration master which allows to tolerate $f$ faults with $f+1$ replicas instead of the traditional $2f+1$ replicas.

@@

\end{document}
    We present a new abstraction, Abortable Generalized Consensus, which enables the
    correct-by-construction composition of heterogeneous State-Machine
    Replication algorithms.

@@

\begin{thm}[Composition Theorem]
    \label{thm:comp}
    In every execution of a succession of ACA rounds, the sequence of valuations
    of the variable $proposed$ and, for every learner $l$, of the variables
    $learned\left[ l \right]$ satisfies Chain Agreement.
\end{thm}
\Cref{thm:comp} can be shown by induction on the number of rounds,
using the following lemma.
\begin{lem}
  \label{lem:comp}
    Consider two rounds numbered $i$ and $i+1$. In every execution of a
    succession of ACA rounds, the sequence of valuations of the variables $inits
    = inits_i$, $propose = proposed_i \cup propose_{i+1}$, for every learner
    $l$, $learned\left[ l \right] = learned_i\left[ l \right] \cup
    learned_{i+1}\left[ l \right]$and $aborts = aborts_{i+1}$ satisfies ACA.
\end{lem}
\begin{proof}
  A mechanically-checked proof in Isabelle/HOL appears in \cref{sec:isaproofs}.
  The proofs uses a version of the specification of ACA that has a more
  executable form that presented in this section. Moreover,
  instead of sequences of commands, the Isabelle/HOL specification uses the more
  general notion of command history, presented in the next subsection.
  The Isabelle/HOL formalization of ACA uses the theory of I/O-automata, which
  is also formalized in the Isabelle/HOL development. The proof uses a refinement
  mapping from the composition of two consecutive ACA instances to a single ACA
  instance.
\end{proof}

@@

Each Classic Paxos round has a unique leader among the acceptors which
centrally orders the proposed commands, which are accepted by the
other acceptors in the order determined by the leader.  This protocol
ensures that every local acceptor history is a prefix of the local
history of the leader, therefore guaranteeing that the local acceptor histories
form a chain.

Each acceptor broadcasts each newly accepted history to the learners, which
learn a history $h$ when they receive enough extensions of $h$ from the
acceptors.  When instructed by the scheduling policy to abort, a
switcher sends a stop message to the acceptors, which irrevocably stop
updating their local history and send back to the switcher an
acknowledgement containing their local history. A switcher
determines an abort history once it has received acknowledgments from
an abort quorum of acceptors $R$, using the operator $SafeAborts\left(
R \right)$.

@@

acceptors of the preceeding rounds, whereas in ACA rounds, the
